04_DESeq_sexes

### 2019-12-23 analysis/04_LDA.Rmd
so many lda plots

```{r LDAplots}
library(kableExtra)
#myshapes = c("hypothalamus" = 20,  "pituitary" = 17,  "gonads" = 15)

@@

plot_grid(a,b,c,d,e,f, nrow = 3)
```

>>>>

```{r LDAplots}
library(kableExtra)

LDA.hyp$treatment <- factor(LDA.hyp$treatment, levels = alllevels)
LDA.hyp$predictedstage <- factor(LDA.hyp$predictedstage, levels = alllevels)

LDA.pit$treatment <- factor(LDA.pit$treatment, levels = alllevels)
LDA.pit$predictedstage <- factor(LDA.pit$predictedstage, levels = alllevels)

LDA.gon$treatment <- factor(LDA.gon$treatment, levels = alllevels)
LDA.gon$predictedstage <- factor(LDA.gon$predictedstage, levels = alllevels)

#myshapes = c("hypothalamus" = 20,  "pituitary" = 17,  "gonads" = 15)

@@

plot_grid(a,b,c,d,e,f, nrow = 3)

g <- ggplot(LDA.hyp, aes(x = LD1, LD2, shape = predictedstage, color = treatment)) + 
  geom_point( ) + theme_B3() +
  theme(legend.position = "none") + 
  scale_color_manual(values = colorscharmaip) + 
  guides(color = guide_legend(show = FALSE))  +
  labs(subtitle = "hypothalamus")

h <- ggplot(LDA.pit, aes(x = LD1, LD2, shape = predictedstage, color = treatment)) + 
  geom_point( ) + theme_B3() +
  theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)  + 
  guides(color = guide_legend(show = FALSE)) +
  labs(subtitle = "piuitary")

i <- ggplot(LDA.gon, aes(x = LD1, LD2, shape = predictedstage, color = treatment)) + 
  geom_point( ) + theme_B3() +
  theme(legend.position = "right") + scale_color_manual(values = colorscharmaip)  + 
  #guides(color = guide_legend(show = FALSE)) +
  guides(shape = guide_legend(ncol = 3),
         color = guide_legend(ncol = 3)) +
  labs(subtitle = "gonads")

gh <- plot_grid(g,h, nrow = 1)
ghi <- plot_grid(gh, i, nrow = 2)
ghi

plotfacetresults <- function(df, whichgroups, mysubstitle, myshape){

  p <- df %>%
    filter(treatment %in% whichgroups) %>%
    ggplot(aes(x = LD1, LD2,  color = predictedstage)) + 
  geom_point(shape = myshape ) + theme_B3() +
    stat_ellipse() +
  theme(legend.position = "none") + 
  scale_color_manual(values = colorscharmaip) + 
  guides(color = guide_legend(show = FALSE))  +
  labs(y = mysubstitle) + 
  facet_wrap(~treatment, nrow = 1)
  return(p)
}

j <- plotfacetresults(LDA.gon, levelstiming, "hypothalamus\n LD2", 20) + labs(x = NULL)
k <- plotfacetresults(LDA.pit, levelstiming, "pituitary\n LD2", 17) + theme(strip.text = element_blank()) + labs(x = NULL)
l <- plotfacetresults(LDA.gon, levelstiming, "gonads\n LD2", 15) + theme(strip.text = element_blank()) + 
  theme(legend.position = "bottom") +
  guides(color = guide_legend(nrow  = 1))

plot_grid(j,k,l, nrow = 3, rel_heights = c(1.2,1,1.6), align = "v")

m <- plotfacetresults(LDA.gon, levelsremoval, "hypothalamus\n LD2", 20) + labs(x = NULL)
n <- plotfacetresults(LDA.pit, levelsremoval, "pituitary\n LD2", 17) + theme(strip.text = element_blank()) + labs(x = NULL)
o <- plotfacetresults(LDA.gon, levelsremoval, "gonads\n LD2", 15) + theme(strip.text = element_blank()) + 
  theme(legend.position = "bottom") +
  guides(color = guide_legend(nrow  = 1))

plot_grid(m,n,o, nrow = 3, rel_heights = c(1.2,1,1.6), align = "v")

plotfacetresults2 <- function(df, whichgroups, mysubstitle, myshape){
  p <- df %>%
    filter(treatment %in% whichgroups) %>%
  ggplot(aes(x = treatment, fill = predictedstage)) +
  geom_bar(position = position_fill(reverse = F))  +
  facet_wrap(~sex) +
    theme_B3() +
  theme(legend.position = "none") +
  scale_fill_manual(values = colorscharmaip) +
  labs(y = mysubstitle) 
  return(p)
}

j <- plotfacetresults2(LDA.gon, levelstiming, "hypothalamus", 20) + labs(x = NULL) + theme(axis.text.x = element_blank()) +
  theme(legend.position = "bottom") + guides(fill = guide_legend(nrow  = 1)) 
k <- plotfacetresults2(LDA.pit, levelstiming, "pituitary", 17) + theme(strip.text = element_blank()) + labs(x = NULL) + theme(axis.text.x = element_blank())
l <- plotfacetresults2(LDA.gon, levelstiming, "gonads", 15) + theme(strip.text = element_blank()) + 
   labs(x = NULL)

plot_grid(j,k,l, nrow = 3, rel_heights = c(1.6,1,1.2))

m <- plotfacetresults2(LDA.gon, levelsremoval, "hypothalamus", 20) + labs(x = NULL) + theme(axis.text.x = element_blank()) +
    theme(legend.position = "top")  +  guides(fill = guide_legend(nrow  = 1))
n <- plotfacetresults2(LDA.pit, levelsremoval, "pituitary", 17) + theme(strip.text = element_blank()) + labs(x = NULL) + theme(axis.text.x = element_blank())
o <- plotfacetresults2(LDA.gon, levelsremoval, "gonads", 15) +
  theme(strip.text = element_blank())  + labs(x = NULL)

plot_grid(m,n,o, nrow = 3, rel_heights = c(1.6,1,1.2))

```
